### 2024-08-27 paper/Cover_letter_Indecisions.tex
changes for plos comp bio

We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{``Indecision under time pressure arises from suboptimal switching behaviour''}}, for publication in \emph{Proceedings of the National Academy of Sciences}.

>>>>

We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{PLOS Computational Biology}.

### 2024-08-27 paper/main.tex
changes for plos comp bio

\noindent \textsuperscript{1} Department of Biomedical Engineering, University of Delaware\\
\textsuperscript{2} Department of Mechanical Engineering, University of Delaware\\
\textsuperscript{3} Biomechanics and Movements Science Program, University of Delaware\\
\textsuperscript{4} Department of Electrical and Computer Engineering, Northeastern University\\
\textsuperscript{5} College of Osteopathic Medicine, New York Institute of Technology\\
\textsuperscript{6} Department of Kinesiology, McMaster University\\
\textsuperscript{7} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
\vspace{1mm}
\\
\textcolor{mydarkblue}{\large Abbreviated Title:}
\vspace{1mm}
\\
Indecision arises from suboptimal switching behaviour
\\
\vspace{1mm}
\\
% \textcolor{mydarkblue}{\large Significance Statement:}
% \vspace{1mm}
% \\
% Indecisive behaviour is highly prevalent in many aspects of daily life. Despite its ubiquity, there has been very little focus and a lack of explanation for why indecisions occur. Here we find under high time pressure scenarios that indecisions arise by misrepresenting additional time delays and temporal uncertainties associated when attempting to switch from reacting to guessing. Our novel paradigm presents a new way to elucidate and study indecisions.
% \\
\\
\textcolor{mydarkblue}{\large Funding:}
\vspace{1mm}
\\
National Science Foundation (NSF \#2146888) awarded to JGAC
\\
National Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589) awarded to MJC
\\
\vspace{1mm}
\\
\textcolor{mydarkblue}{\large Correspondence:}
\\
Seth Sullivan\\
Biomedical Engineering\\
University of Delaware\\
Newark, DE 19711, U.S.A\\
Email: sethsullivan99@gmail.com
\\
\\
Joshua G. A. Cashaback, PhD\\
Biomedical Engineering\\
University of Delaware\\
STAR Campus, Room 201J\\
Newark, DE 19711, U.S.A\\
Email: cashabackjga@gmail.com

@@

There have only been a handful of papers to examine indecisions, which involve either high \autocite{lokeshHumansUtilizeSensory2022} or low time pressure \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016,philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}. We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokeshHumansUtilizeSensory2022}. In this competitive scenario, the ‘prey’ attempted to end up in the same target as the ‘predator’ by a time constraint, while the predator attempted to end up in the opposite target as the prey. This task had a high time pressure, such that participants were awarded no points if they were indecisive by failing to enter either target within the time constraint. The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision. Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions. Similar to others \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016, philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions. Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline. Yet the mechanisms that give rise to indecisive behaviour, which is particularly relevant under common high time pressure scenarios, remains unclear.

>>>>

\noindent \textsuperscript{1} Department of Biomedical Engineering, University of Delaware\\
\textsuperscript{2} Department of Mechanical Engineering, University of Delaware\\
\textsuperscript{3} Biomechanics and Movements Science Program, University of Delaware\\
\textsuperscript{4} Department of Electrical and Computer Engineering, Northeastern University\\
\textsuperscript{5} College of Osteopathic Medicine, New York Institute of Technology\\
\textsuperscript{6} Department of Kinesiology, McMaster University\\
\textsuperscript{7} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
\vspace{1mm}
\\
\textcolor{mydarkblue}{\large Abbreviated Title:}
\vspace{1mm}
\\
Indecision arises from suboptimal switching behaviour
\\
\vspace{1mm}
\\
\textcolor{mydarkblue}{\large Author Summary:}
\vspace{1mm}
\\
Indecisive behaviour is highly prevalent in many aspects of daily life. Despite its ubiquity, there has been very little focus and a lack of explanation for why indecisions occur. Here we find under high time pressure scenarios that indecisions arise by misrepresenting additional time delays and temporal uncertainties associated when attempting to switch from reacting to guessing. Our novel paradigm presents a new way to elucidate and study indecisions.
\\
\\
\textcolor{mydarkblue}{\large Funding:}
\vspace{1mm}
\\
National Science Foundation (NSF \#2146888) awarded to JGAC
\\
National Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589) awarded to MJC
\\
\vspace{1mm}
\\
\textcolor{mydarkblue}{\large Correspondence:}
\\
Seth Sullivan\\
Biomedical Engineering\\
University of Delaware\\
Newark, DE 19711, U.S.A\\
Email: sethsullivan99@gmail.com
\\
\\
Joshua G. A. Cashaback, PhD\\
Biomedical Engineering\\
University of Delaware\\
STAR Campus, Room 201J\\
Newark, DE 19711, U.S.A\\
Email: cashabackjga@gmail.com

@@

There have only been a handful of papers to examine indecisions, which involve either high \autocite{lokeshHumansUtilizeSensory2022} or low time pressure \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016,philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}. We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokeshHumansUtilizeSensory2022}. In this competitive scenario, the ‘predator’ attempted to end up in the same target as the ‘prey’ by a time constraint, while the prey attempted to end up in the opposite target as the predator. This task had a high time pressure, such that participants were award ed no points if they were indecisive by failing to enter either target within the time constraint. The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision. Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions. Similar to others \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016, philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions. Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline. Yet the mechanisms that give rise to indecisive behaviour, which is particularly relevant under common high time pressure scenarios, remains unclear.
